Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-14 Thesis/chapter/033-linreg-krr-svm.tex
finish kernel

%\textbf{Kernel Ridge Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%% { Kernel Ridge Regression } KRR %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{\gls{krr}} combines ridge regression with the kernel method. 
A~kernel transforms data in such a way that a linear hyperplane (a line in one dimension, 
a plane in two dimensions) can fit data in regression problems or seperate the data in classification problems. 
A kernel is some kind of similarity measure 
which fulfills the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
The following equations show definitions for 
linear (eq.~\ref{eq:lin-kernel}), 
polynomial (eq.~\ref{eq:pol-kernel}), 
sigmoidal (eq.~\ref{eq:sig-kernel}) and 
radial basis functionial kernel~(eq. \ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
\begin{align}
    \label{eq:lin-kernel}
    k_{lin}(\mathbf{x},\mathbf{y}) &= \mathbf{x}^{\top} \mathbf{y} \\
    \label{eq:pol-kernel}
    k_{pol}(\mathbf{x}, \mathbf{y}) &= (\gamma \mathbf{x}^{\top} \mathbf{y} + c_0)^d \\
    \label{eq:sig-kernel}
    k_{sig}(\mathbf{x}, \mathbf{y}) &= \text{tanh}(\gamma \mathbf{x}^{\top} \mathbf{y} + c_0) \\
    \label{eq:rbf-kernel}
    k_{rbf}(\mathbf{x}, \mathbf{y}) &= \text{exp}(- \gamma \| \mathbf{x} -  \mathbf{y} \|^2) 
\end{align}
A requirement for using kernels is having a dot product in the loss function. 
This can be accomplished by expressing $\mathbf{k}$ with $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
\cite{rudin2020least}

@@

\textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 

@@

By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function: 

@@

	\mathcal{L} = \frac{1}{2} \|\mathbf{w}\| - \sum_i^n \alpha_i [ y_i ( w_i \cdot x_i + b) -1 ] 

@@

$\frac{\partial \mathcal{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathcal{L}}{\partial b}$ 

@@

	\mathcal{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_j^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 

@@

\Gls{svm}s can handle non-perfect data by introducing a penalization for wrongly categorized samples. 

@@

    L_H = sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 

@@

if the prediction and the true category don't agree, they have opposite signs and 
their product will be a negative number.
This is called a soft-margin \gls{svm} in contrast to the previously hard-margin \gls{svm}.

A big advantage of \gls{svm} is that through the kernel trick non-linearly separable data 
can be divided. 
\td{write about kernel trick and non strick}

>>>>

%\textbf{Kernel Ridge Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%% { Kernel Ridge Regression } KRR %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{\gls{krr}} combines ridge regression with the kernel method. 
A~kernel transforms data in such a way that a linear hyperplane (a line in two dimensions, 
a plane in three dimensions) can fit data in regression problems or seperate the data in classification problems without actually doing the transormation for every data point. 
A kernel is some kind of similarity measure 
which fulfills the requirements of nonnegativity, symmetry, linearity\cite{rupp2015machine}.
The following equations show definitions for 
linear (eq.~\ref{eq:lin-kernel}), 
polynomial (eq.~\ref{eq:pol-kernel}), 
sigmoidal (eq.~\ref{eq:sig-kernel}) and 
radial basis functionial kernel~(eq. \ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
\begin{align}
    \label{eq:lin-kernel}
    k_{lin}(\mathbf{x},\mathbf{y}) &= \mathbf{x}^{\top} \mathbf{y} \\
    \label{eq:pol-kernel}
    k_{pol}(\mathbf{x}, \mathbf{y}) &= (\gamma \mathbf{x}^{\top} \mathbf{y} + c_0)^d \\
    \label{eq:sig-kernel}
    k_{sig}(\mathbf{x}, \mathbf{y}) &= \text{tanh}(\gamma \mathbf{x}^{\top} \mathbf{y} + c_0) \\
    \label{eq:rbf-kernel}
    k_{rbf}(\mathbf{x}, \mathbf{y}) &= \text{exp}(- \gamma \| \mathbf{x} -  \mathbf{y} \|^2) 
\end{align}
A requirement for using kernels is having a dot product in the loss function. 
This can be accomplished by expressing $\mathbf{k}$ with $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
\cite{rudin2020least}.

@@

\textbf{\Gls{svm}} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training} . 

@@

By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function which should be maximized: 

@@

	\mathfrak{L} = \frac{1}{2} \|\mathbf{w}\|^2 - \sum_i^n \alpha_i [ y_i ( w_i \cdot x_i + b) -1 ] 

@@

$\frac{\partial \mathfrak{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathfrak{L}}{\partial b}$ 

@@

	\label{eq:svm04}
	\mathfrak{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_j^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 

@@

%%%%%%%%%% SOFT MARGIN SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Soft margin \gls{svm}} - in contrast to hard margin \gls{svm} is used if the data is non-seperable due to outliers\cite{cortes1995support}.
Such data can be handeled by introducting a penalization term for wrongly categorized samples into the loss function. 

@@

	\label{eq:svm-soft}
	L_{SM} = \frac{2} {\|\mathbf{w}\|} + \sum_i^n max(0, 1- y_i ( \mathbf{w} \mathbf{x}_i + b ) 

@@

If the prediction $\mathbf{w}\mathbf{x}_i+b$ and the true category $y_i$ don't agree, 
they have opposite signs and their product will be a negative number.
The substraction of a negative number will result in a positive penalizisation. 
If the sample iis correctly predicted, the product will result in a positive number, 
the substraction in a negative number and the maximum will be 0, if the sample is ousite of the margin.

%%%%%%%%%%% KERNELS IN SVM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%A big advantage of \gls{svm} is that through the kernel trick non-linearly separable data can be divided. 
%As mentioned before, a inner product is need to use the kernel trick. 
The function we want to optimize (see eq. \ref{eq:svm04}) and its soft margin equivalent can both be expressed as inner products. 
This allows us to seperate data not only with hyperplanes 
but also with komplex decision boundaries due to the kernel trick. 
Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper. 
\td{write about sv regrgession}
%\td{write about kernel}
